### 2022-01-06 experiments.tex
writing

We begin with a simple analysis of the stability of the Plant.
\Cref{fig:topple:fraction} shows a visualization of the fraction of plants that toppled in each scenario.
It provides a very clear overview of the minimum requirements

@@

>>>>

We begin with a simple analysis of the stability of the Plant, as \ac{CLEAVE} allows for straightforward and repeatable analysis of relevant metrics.  
For instance, \cref{fig:topple:fraction} shows a visualization of the fraction of plants that toppled in each scenario.
These Plants were identified simply by analyzing the emulation data --- instances whose pendulum angles reached values above a certain value\footnote{This value will depend on the parametrization of the controller, and in this case corresponds to \SI{20}{\degree}, or \SI{0.35}{\radian}} were marked as ``toppled''.

@@

\Ac{CLEAVE} also allows for more fine-grained analysis of stability.
\Cref{fig:topple:rms} shows the \ac{RMS} of the angles for each setup, averaged over all repetitions of each experiment.

\begin{figure}
    \centering
    \includegraphics[width=.8\columnwidth]{angle_rms.png}
    \caption{RMS}%
    \label{fig:topple:rms}
\end{figure}
